Response to the defense feedback

### 2021-06-19 Chapter-4/Chapter-4.tex
Updates from Overleaf

\begin{theorem}
    \label{IndependentConstraint}
    Let $g_{1}, g_{2}, \ldots, g_{m}$ be a maximum independent partition of
    $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
    $K_c$ is the input set that satisfies constraint $c$. We have the following
    equation with regard to the size of $K_c$
    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}| \cdot |K_{g_{2}}| \cdot \ldots \cdot|K_{g_{n}}|$$
\end{theorem}
With Theorem~\ref{IndependentConstraint}, we change the problem of counting the number of solutions to a complicated constraint in a high-dimension
space into counting solutions to several small constraints. We compute the maximum independent partition by iterating each $\addr{i}$ and applying the function $\pi$ over the constraint $\addr{i}$.

>>>>

\begin{theorem}
    \label{IndependentConstraint}
    Let $g_{1}, g_{2}, \ldots, g_{m}$ be a maximum independent partition of
    $c_t(\addr{1},\addr{2},\ldots,\addr{n})$.
    $K_c$ is the input set that satisfies constraint $c$. We have the following
    equation with regard to the size of $K_c$
    $$|K_{c_t(\addr{1},\addr{2},\ldots,\addr{n})}| = |K_{g_{1}}| \cdot |K_{g_{2}}| \cdot \ldots \cdot|K_{g_{n}}|$$
\end{theorem}
With Theorem~\ref{IndependentConstraint}, we transfer the problem of counting the number of solutions to a complicated constraint in a high-dimension
space into counting solutions to several small constraints. We compute the maximum independent partition by iterating each $\addr{i}$ and applying the function $\pi$ over the constraint $\addr{i}$.
